Self Regulation Ontology Retest Data Report

### 2017-04-21 SRO_Report.Rmd
began writing bootstrapping code

get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  df = df %>% spread(time, score) %>% select(-dv, -sub_id)
  icc = ICC(df)
  icc_3k = icc$results['Average_fixed_raters', 'ICC']
  return(icc_3k)
  }

get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
  eta = ss_time/(ss_time+ss_error)
  return(eta)
  }

get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
  sem = sqrt(ms_error)
  return(sem)
}
```

@@

>>>>

get_icc <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
  if(match==TRUE){
    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var, format='wide')
  }
  else{
    df = matched_df
  }
  df = df %>% select(-dv, -sub_id)
  icc = ICC(df)
  icc_3k = icc$results['Average_fixed_raters', 'ICC']
  return(icc_3k)
  }

get_eta <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
  if(match==TRUE){
    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  }
  else{
    df = matched_df
  }
  mod = summary(aov(score~Error(sub_id)+time, df))
  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
  eta = ss_time/(ss_time+ss_error)
  return(eta)
  }

get_sem <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', match=TRUE, matched_df){
  if(match==TRUE){
    df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  }
  else{
    df = matched_df
  }
  mod = summary(aov(score~Error(sub_id)+time, df))
  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
  sem = sqrt(ms_error)
  return(sem)
}
```

@@

Bootstrapping

```{r}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

extract_sample_data = function(sample, var_name, df, worker_col = "sub_id"){
  return(df[df[,worker_col] %in% sample, var_name])
}

sample_workers()
extract_sample_data(df=retest_data)
extract_sample_data(df=retest_subs_test_data)
```
